---
title: "Schweihs_8_r_3"
author: "Maggie Schweihs"
date: "10/29/2016"
output: pdf_document
---
#3. Sentence Length v. Word Length
*Investigate whether sentences with more words tend to contain longer words.*

####3.a: Load the data set into R and make a scatterplot of mean length of words versus number of words per sentence.

```{r}
pride <- read.csv("~/Documents/Code/DS710/ds710fall2016assignment7/pride.csv", header = TRUE)
attach(pride)
plot(mean_word_length ~ word_count, type = "p", lwd = .4, main = "Scatterplot: Mean Word Length vs. Word Count")
```
**Does Linear Regression make sense here?**

Looking at the scatterplot of mean length of words versus number of words per sentence, the data appears to have a polynomial relationship, due to one or more noticable humps on the graph. Linear regressions **would not** be appropriate here.

###3.b: Trial and Error
For lack of a better method, I tried various combinations of variables and transformations of variables: logarithmic transformation, quadratic functions, cubic functions, and combinations therein. Below is a subset of that trial and error. Along the way I did **Not** wind up with anything appearing to be linear.
```{r}
# For Lack of knowledge of a statistical tool to measure and compare
# relationships between variables, I resorted to good ole trial and error

#Initializing some variables to store the functions and transformations
pride_cubic_length <- (mean_word_length + (mean_word_length)^3 +(mean_word_length)^2)
pride_cubic_count <- (word_count + (word_count)^3 +(word_count)^2)
pride_quad_count <- (word_count +(word_count)^2)
pride_quart_length <- ((mean_word_length)^4 + (mean_word_length)^3 +(mean_word_length)^2 + mean_word_length)
pride_quad_length <- (mean_word_length +(mean_word_length)^2)
log_length <- log(mean_word_length)
log_count <- log(word_count)
#plot some Combinations
plot(mean_word_length~pride_quad_count, main = "Mean Word Length versus Word Count(Quadratic)" )
plot(log_length~word_count, main = "Mean Word Length (Log) versus Word Count" )
```

Neither one of the above transformations yielded a plot appropriate for linear regression

####3.c: c.	Test whether sentences with more words tend to contain longer words.  State your conclusion in context.I'm going to test the relationship between `mean_word_length` and the quadratic word count function.

H_0: Longer sentences do not typically have longer words in Pride and Prejudice. mu = 0

H_1: Longer sentences **do** have longer words in Pride and Prejudice. mu != 0

Test using the significance test for linear regression.

```{r}
pride.lm <- lm(mean_word_length~pride_quad_count)
pride.lm
summary(pride.lm)
```

The p-value for the test is p=0.7164, so we **cannot** reject the null hypothesis. There is not significant evidence here to suggest a relationship between mean word length and the number of words in a sentence.

####3.d: Add a line to my scatterplot representing the regression model.

```{r}
plot(mean_word_length~pride_quad_count, main = "Mean Word Length versus Word Count(Quadratic)" )
abline(lm(mean_word_length~pride_quad_count), col = "red", cex =1)
legend("topright", c("Linear Regression Model"), col ="red", pch = 21)
```


The slope of the linear regression line is roughly 0.007 and is shown to be non-significant. We can see this by observe the graph, as well. The slope of the line is nearly zero, which reaffirms the result of the significance test: we did not show a linear relationship between the variables with this model. Recommendation: ecplore non-linear models.

####3.e: Examine the residual diagnostic plots, and explain what they tell us in this case.

```{r}
par( mfrow = c( 2, 2 ) )
plot(pride.lm)
```

By looking at the Residuals versus Fitted plot, we reaffirm the intuition that some affects of the dependent variable are not being taken into account by our model.The Normal Q-Q plot suggests that our data is right-skewed and possibly bi-modal.